Paper figures

### 2018-12-02 voltagebudget/analysis/fixed_run_time_analysis.Rmd
Update figs

```{r, fig.width=1.5, fig.height=0.7}
avg_results %>%
  ggplot(aes(x=run_time, y=(variances_pop/n_spikes_pop)*1e3, color=freq, group=interaction(freq, run_time))) +
  geom_point(size=1, alpha=0.8) +
  labs(x="Run time (s)", y="Variance (ms)") +
  theme_classic() +
  facet_grid(.~freq) +
  scale_color_gradient2(low="gold", high="darkgreen", mid="grey", midpoint=20, name="Freq. (Hz)") +
  theme(legend.position="right", 
    legend.key.size = unit(.4, "cm"),
    legend.title = element_text(size=8),
    legend.text = element_text(size=8),
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank(),
    strip.background = element_blank(),
    strip.text.x = element_blank()) 
```

# Individual cells
## Error

```{r, fig.width=1.5, fig.height=0.7}
results %>%
  ggplot(aes(x=run_time, y=(errors/n_spikes)*1e3, color=freq, group=interaction(freq, run_time))) +
  # geom_point(size=0.05, alpha=0.2) + 
  geom_boxplot(outlier.size = NA) +
  labs(x="Run time (s)", y="Variance (ms)") +
  theme_classic() +
  facet_grid(.~freq) +
  scale_color_gradient2(low="gold", high="darkgreen", mid="grey", midpoint=20, name="Freq. (Hz)") +
  theme(legend.position="right", 
    legend.key.size = unit(.4, "cm"),
    legend.title = element_text(size=8),
    legend.text = element_text(size=8),
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank(),
    strip.background = element_blank(),
    strip.text.x = element_blank()) 
```

## Var

```{r, fig.width=1.5, fig.height=0.7}
results %>%
  ggplot(aes(x=run_time, y=(variances/n_spikes)*1e3, color=freq, group=interaction(freq, run_time))) +
  # geom_point(size=0.05, alpha=0.2) + 
  geom_boxplot(outlier.size = NA) +
  labs(x="Run time (s)", y="Variance (ms)") +
  theme_classic() +
  facet_grid(.~freq) +
  scale_color_gradient2(low="gold", high="darkgreen", mid="grey", midpoint=20, name="Freq. (Hz)") +
  theme(legend.position="right", 
    legend.key.size = unit(.4, "cm"),
    legend.title = element_text(size=8),
    legend.text = element_text(size=8),
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank(),
    strip.background = element_blank(),
    strip.text.x = element_blank()) 
```

>>>>

```{r, fig.width=1.5, fig.height=0.9}
avg_results %>%
  ggplot(aes(x=run_time, y=(variances_pop/n_spikes_pop)*1e3, color=freq, group=interaction(freq, run_time))) +
  geom_point(size=0.3, alpha=0.9) +
  labs(x="Run time (s)", y="Avg. variance (ms)") +
  theme_classic() +
  scale_color_gradient2(low="gold", high="darkgreen", mid="grey", midpoint=20, name="Freq. (Hz)") +
  theme(legend.position="right", 
    legend.key.size = unit(.4, "cm"),
    legend.title = element_text(size=8),
    legend.text = element_text(size=8),
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank(),
    strip.background = element_blank(),
    strip.text.x = element_blank()) 
```

# Individual cells

```{r, fig.width=2.5, fig.height=2.7}
results %>%
  filter(As < 0.05e-9) %>% 
  ggplot(aes(x=As, y=(variances/n_spikes)*1e3, color=run_time, group=interaction(As, run_time))) +
  # geom_point(size=0.05, alpha=0.1) +
  geom_boxplot(outlier.size = NA) +
  labs(x="A (namp)", y="Variance (ms)") +
  theme_classic() +
  facet_grid(freq~.) +
  scale_color_gradient(low="blue", high="darkgreen") +
  lims(y=c(0, 20)) +
  theme(legend.position="bottom", 
    legend.key.size = unit(.4, "cm"),
    legend.title = element_text(size=8),
    legend.text = element_text(size=8),
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank(),
    strip.background = element_blank(),
    strip.text.x = element_blank()) 
```

### 2018-12-02 voltagebudget/analysis/paper_figures.Rmd
Update figs

---
title: "Exp1 - Opt w_max and {A,phi)"
output: html_notebook
---

@@

```{r, fig.width=3, fig.height=1.6}
min_t <- min(fig4$ts)

@@

fig3 %>% 
  filter(alg != "coincidence", alg != "left") %>%
  ggplot(aes(x=errors*1e3, y=obs_variances*1e3, color=alg)) +
  geom_line(size=0.8, alpha=0.8) +
  scale_color_brewer(palette = "Set1", name="Algorithm:") +
  theme_classic() +
  labs(x="Time (ms)", y="Neuron") +
  theme(legend.position="bottom",
    legend.key.size = unit(.5, "cm"),
    legend.title = element_text(size=10),
    legend.text = element_text(size=10),
    legend.background = element_rect(colour ="black")) +
  labs(x="Error (ms)", y="Variance (ms)") -> p2

plot_grid <- rbind(
  # c(1, 1, 1, NA, NA, NA, NA),
  c(1, 1, 1, 2, 2, 2, 2),
  c(1, 1, 1, 2, 2, 2, 2),
  c(1, 1, 1, 2, 2, 2, 2),
  c(1, 1, 1, 2, 2, 2, 2),
    c(NA, NA, NA, 2, 2, 2, 2))
  # c(1, 1, 1, 2, 2, 2, 2),
  # c(NA, NA, NA, 2, 2, 2, 2))

>>>>

---
title: "Paper figures"
output: html_notebook
---

@@

```{r, fig.width=1.2, fig.height=2}
min_t <- min(fig4$ts)

@@

fig3 %>% 
  filter(alg != "coincidence", alg != "left") %>%
  ggplot(aes(x=errors*1e3, y=obs_variances*1e3, color=alg)) +
  geom_line(size=0.8, alpha=0.8) +
  scale_color_brewer(palette = "Set1", name="Algorithm:") +
  theme_classic() +
  labs(x="Time (ms)", y="Neuron") +
  theme(legend.position="bottom",
    legend.key.size = unit(.2, "cm"),
    legend.title = element_text(size=10),
    legend.text = element_text(size=10),
    legend.background = element_rect(colour ="black")) +
  labs(x="Error (ms)", y="Variance (ms)") -> p2

plot_grid <- rbind(
  c(1),
  c(1),
  c(2),
  c(2),
  c(2))
